---
title: "Diatom_Time_Course_all_Consolidations"
author: "Idan Siman-Tov"
date: '2022-11-07'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
library(xlsx)
library(ggplot2)
library(ggfortify)
library(tidyverse)
library(dplyr)
library(GGally)
library(corrgram)
library(janitor)
library(reshape2)
library(ggpubr)
library(ggnewscale)

```


```{r}

# no

source("..//..//Functions//My_Functions.R")
# source("..//..//Functions//minimum_consolidation_functions//data_for_pca_formating_updatedSept2022_no_percentage_minimum_consolidation.R")
source("..//..//Functions//no_consolidation_functions//metagenome_taxa_removed_updatedSept2022_no_percentage_no_consolidation.R")

# source("..//..//Functions//minimum_consolidation_functions//Taxa_DF_updatedSept2022_no_percentage_minimum_consolidation.R")

```

```{r}
# data_for_pca<-data_for_pca()
metagenome_taxa<-metagenome_taxa_removed()
```

```{r}
metagenome_taxa_percentage <-Percentage_Function(metagenome_taxa)
```

```{r}
# Format the table for ggplot
metagenome_taxa_count_time_course<-setNames(melt(metagenome_taxa), c('Taxa', 'Date', 'Percent_of_Population'))
metagenome_taxa_percentage_time_course<-setNames(melt(metagenome_taxa_percentage), c('Taxa', 'Date', 'Percent_of_Population'))
```

```{r}
# Convert numbers to log base 10 so that its easier to graph
# Converting Percent_of_Population to logs
metagenome_taxa_count_time_course_log<- metagenome_taxa_count_time_course
metagenome_taxa_count_time_course_log$Percent_of_Population<-log10(metagenome_taxa_count_time_course_log$Percent_of_Population)


# Converting percentages to logs
metagenome_taxa_percentage_time_course_log<- metagenome_taxa_percentage_time_course
metagenome_taxa_percentage_time_course_log$Percent_of_Population<-log10(metagenome_taxa_percentage_time_course_log$Percent_of_Population)

```

```{r}
# Filtering to only include the "large correlated taxa" from percentages
No_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Stramenopiles.Diatomea.Bacillariophytina|Stramenopiles.Diatomea.Coscinodiscophytina|Stramenopiles.Diatomea.otherDiatomea|Stramenopiles.Diatomea.ME-Euk-FW10|Stramenopiles.Dictyochophyceae.Dictyochales|Stramenopiles.Dictyochophyceae.otherDictyochophyceae|Stramenopiles.Dictyochophyceae.Florenciellales|Stramenopiles.Dictyochophyceae.Pedinellales"))
```




"Stramenopiles.Diatomea.Bacillariophytina|Stramenopiles.Diatomea.Coscinodiscophytina|Stramenopiles.Diatomea.otherDiatomea|Stramenopiles.Diatomea.ME-Euk-FW10"




```{r}

# minimum

# source("..//..//Functions//My_Functions.R")
source("..//..//Functions//minimum_consolidation_functions//data_for_pca_formating_updatedSept2022_no_percentage_minimum_consolidation.R")
source("..//..//Functions//minimum_consolidation_functions//metagenome_taxa_removed_updatedSept2022_no_percentage_minimum_consolidation.R")

source("..//..//Functions//minimum_consolidation_functions//Taxa_DF_updatedSept2022_no_percentage_minimum_consolidation.R")

```

```{r}
data_for_pca<-data_for_pca()
metagenome_taxa<-metagenome_taxa_removed()
```

```{r}
metagenome_taxa_percentage <-Percentage_Function(metagenome_taxa)
```

```{r}
# Format the table for ggplot
metagenome_taxa_count_time_course<-setNames(melt(metagenome_taxa), c('Taxa', 'Date', 'Percent_of_Population'))
metagenome_taxa_percentage_time_course<-setNames(melt(metagenome_taxa_percentage), c('Taxa', 'Date', 'Percent_of_Population'))
```

```{r}
# Convert numbers to log base 10 so that its easier to graph
# Converting Percent_of_Population to logs
metagenome_taxa_count_time_course_log<- metagenome_taxa_count_time_course
metagenome_taxa_count_time_course_log$Percent_of_Population<-log10(metagenome_taxa_count_time_course_log$Percent_of_Population)


# Converting percentages to logs
metagenome_taxa_percentage_time_course_log<- metagenome_taxa_percentage_time_course
metagenome_taxa_percentage_time_course_log$Percent_of_Population<-log10(metagenome_taxa_percentage_time_course_log$Percent_of_Population)

```

```{r}
# Filtering to only include the "large correlated taxa" from percentages
Minimum_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Stramenopiles.Diatomea.Bacillariophytina|Stramenopiles.Diatomea.Coscinodiscophytina|Stramenopiles.Diatomea.otherDiatomea|Stramenopiles.Diatomea.ME-Euk-FW10|Stramenopiles.Dictyochophyceae.Dictyochales.and.Florenciellales.and.otherDictyochophyceae|Stramenopiles.Dictyochophyceae.Pedinellales"))
```



"Stramenopiles.Diatomea.Bacillariophytina|Stramenopiles.Diatomea.Coscinodiscophytina|Stramenopiles.Diatomea.otherDiatomea|Stramenopiles.Diatomea.ME-Euk-FW10"








```{r}
# medium


# source("..//..//Functions//My_Functions.R")
source("..//..//Functions//medium_consolidation_functions//data_for_pca_formating_updatedSept2022_no_percentage_medium_consolidation.R")
source("..//..//Functions//medium_consolidation_functions//metagenome_taxa_removed_updatedSept2022_no_percentage_medium_consolidation.R")

source("..//..//Functions//medium_consolidation_functions//Taxa_DF_updatedSept2022_no_percentage_medium_consolidation.R")



```

```{r}
data_for_pca<-data_for_pca()
metagenome_taxa<-metagenome_taxa_removed()
```

```{r}
metagenome_taxa_percentage <-Percentage_Function(metagenome_taxa)
```

```{r}
# Format the table for ggplot
metagenome_taxa_count_time_course<-setNames(melt(metagenome_taxa), c('Taxa', 'Date', 'Percent_of_Population'))
metagenome_taxa_percentage_time_course<-setNames(melt(metagenome_taxa_percentage), c('Taxa', 'Date', 'Percent_of_Population'))
```

```{r}
# Convert numbers to log base 10 so that its easier to graph
# Converting Percent_of_Population to logs
metagenome_taxa_count_time_course_log<- metagenome_taxa_count_time_course
metagenome_taxa_count_time_course_log$Percent_of_Population<-log10(metagenome_taxa_count_time_course_log$Percent_of_Population)


# Converting percentages to logs
metagenome_taxa_percentage_time_course_log<- metagenome_taxa_percentage_time_course
metagenome_taxa_percentage_time_course_log$Percent_of_Population<-log10(metagenome_taxa_percentage_time_course_log$Percent_of_Population)

```

```{r}
# Filtering to only include the "large correlated taxa" from percentages
Medium_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Stramenopiles.Diatomea.Bacillariophytina.and.Coscinodiscophytina.and.otherDiatomea|Stramenopiles.Diatomea.ME-Euk-FW10|Stramenopiles.Dictyochophyceae.Dictyochales.and.Florenciellales.and.otherDictyochophyceae|Stramenopiles.Dictyochophyceae.Pedinellales"))
```


"Stramenopiles.Diatomea.Bacillariophytina.and.Coscinodiscophytina.and.otherDiatomea|Stramenopiles.Diatomea.ME-Euk-FW10"




```{r}

# maximum

# source("..//..//Functions//My_Functions.R")
source("..//..//Functions//maximum_consolidation_functions//data_for_pca_formating_updatedSept2022_no_percentage_maximum_consolidation.R")
source("..//..//Functions//maximum_consolidation_functions//metagenome_taxa_removed_updatedSept2022_no_percentage_maximum_consolidation.R")

source("..//..//Functions//maximum_consolidation_functions//Taxa_DF_updatedSept2022_no_percentage_maximum_consolidation.R")

```



```{r}
data_for_pca<-data_for_pca()
metagenome_taxa<-metagenome_taxa_removed()
```

```{r}
metagenome_taxa_percentage <-Percentage_Function(metagenome_taxa)
```

```{r}
# Format the table for ggplot
metagenome_taxa_count_time_course<-setNames(melt(metagenome_taxa), c('Taxa', 'Date', 'Percent_of_Population'))
metagenome_taxa_percentage_time_course<-setNames(melt(metagenome_taxa_percentage), c('Taxa', 'Date', 'Percent_of_Population'))
```

```{r}
# Convert numbers to log base 10 so that its easier to graph
# Converting Percent_of_Population to logs
metagenome_taxa_count_time_course_log<- metagenome_taxa_count_time_course
metagenome_taxa_count_time_course_log$Percent_of_Population<-log10(metagenome_taxa_count_time_course_log$Percent_of_Population)


# Converting percentages to logs
metagenome_taxa_percentage_time_course_log<- metagenome_taxa_percentage_time_course
metagenome_taxa_percentage_time_course_log$Percent_of_Population<-log10(metagenome_taxa_percentage_time_course_log$Percent_of_Population)

```

```{r}
# Filtering to only include the "large correlated taxa" from percentages
Maximum_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Stramenopiles.Diatomea.all|Stramenopiles.Dictyochophyceae.all"))
```


"Stramenopiles.Diatomea.all"












```{r}

```




```{r}
No_consolidation_time_course<- ggplot(No_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("No_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log") +
    theme(axis.text = element_text(angle = -45))
#+
  # theme(axis.text.x=element_blank(),
  #     axis.ticks.x=element_blank(),
  #      axis.title.x=element_blank()) 
      
```



```{r}
Minimum_consolidation_time_course<- ggplot(Minimum_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("Minimum_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log") +
    theme(axis.text = element_text(angle = -45))
# +
#   theme(axis.text.x=element_blank(),
#       axis.ticks.x=element_blank(),
#        axis.title.x=element_blank()) 
      
```





```{r}
Medium_consolidation_time_course<- ggplot(Medium_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("Medium_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log") +
      theme(axis.text = element_text(angle = -45))

# +
#   theme(axis.text.x=element_blank(),
#       axis.ticks.x=element_blank(),
#        axis.title.x=element_blank()) 
      
```




```{r}
Maximum_consolidation_time_course<- ggplot(Maximum_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("Maximum_consolidation_Diaomea_and_Dictyochophyceae_metagenome_taxa_percentage_time_course_log") +
      theme(axis.text = element_text(angle = -45))

# +
#   theme(axis.text.x=element_blank(),
#       axis.ticks.x=element_blank(),
#        axis.title.x=element_blank()) 
#       
```






```{r}
ggarrange(No_consolidation_time_course, Minimum_consolidation_time_course, Medium_consolidation_time_course, Maximum_consolidation_time_course, heights = c(2, 2), ncol = 2, nrow = 2, align = "hv", hjust = 10)+
      theme(plot.margin = margin(0,0,50,0, "pt")) 
```


