---
title: "Taxa_DF"
author: "Idan Siman-Tov"
date: '2022-06-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
# Using an external xlsx file i made of percentages of taxa instead of counts
Metagenome_percent_counts <- read.xlsx("Metagenome_percent_counts.xlsx", sheetIndex=1, header= TRUE)

Metagenome_average_counts_intermidiary<- Metagenome_average_counts

Metagenome_average_counts_intermidiary[1:27,2:20]<-Metagenome_percent_counts[1:27,3:20]

Metagenome_percent_counts<-Metagenome_average_counts_intermidiary
```




```{r}
# Turing the df into a table for ggplot of percentages
Metagenome_Graph_data<-setNames(melt(Metagenome_percent_counts), c('Taxa', 'Date', 'Counts'))
```





Adding the Metagenome data to the PCA df

```{r}
Metagenome_Graph_data_alphabetical <- Metagenome_Graph_data[order(Metagenome_Graph_data$Taxa),]
```






CREATING A DF FOR EACH TAXA

Archaeplastida.Chlorophyta
```{r}
Archaeplastida.Chlorophyta<-function(){
Archaeplastida.Chlorophyta <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Archaeplastida.Chlorophyta")
Archaeplastida.Chlorophyta <- Archaeplastida.Chlorophyta[3]
colnames(Archaeplastida.Chlorophyta)<-"Archaeplastida.Chlorophyta"
return(Archaeplastida.Chlorophyta)
}
```

	
Archaeplastida.otherArchaeplastida
```{r}
Archaeplastida.otherArchaeplastida<-function(){
Archaeplastida.otherArchaeplastida <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Archaeplastida.otherArchaeplastida")
Archaeplastida.otherArchaeplastida <- Archaeplastida.otherArchaeplastida[3]
colnames(Archaeplastida.otherArchaeplastida)<-"Archaeplastida.otherArchaeplastida"
return(Archaeplastida.otherArchaeplastida)
}
```


Cryptophyceae.Cryptomonadales.Geminigera
```{r}
Cryptophyceae.Cryptomonadales.Geminigera<-function(){
Cryptophyceae.Cryptomonadales.Geminigera <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Cryptophyceae.Cryptomonadales.Geminigera")
Cryptophyceae.Cryptomonadales.Geminigera <- Cryptophyceae.Cryptomonadales.Geminigera[3]
colnames(Cryptophyceae.Cryptomonadales.Geminigera)<-"Cryptophyceae.Cryptomonadales.Geminigera"
return(Cryptophyceae.Cryptomonadales.Geminigera)
}
```

Cryptophyceae.otherCryptophyceae
```{r}
Cryptophyceae.otherCryptophyceae<-function(){
Cryptophyceae.otherCryptophyceae <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Cryptophyceae.otherCryptophyceae")
Cryptophyceae.otherCryptophyceae <- Cryptophyceae.otherCryptophyceae[3]
colnames(Cryptophyceae.otherCryptophyceae)<-"Cryptophyceae.otherCryptophyceae"
return(Cryptophyceae.otherCryptophyceae)
}
```

Excavata.Discoba.Jakobida
```{r}
Excavata.Discoba.Jakobida<-function(){
Excavata.Discoba.Jakobida <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Excavata.Discoba.Jakobida")
Excavata.Discoba.Jakobida <- Excavata.Discoba.Jakobida[3]
colnames(Excavata.Discoba.Jakobida)<-"Excavata.Discoba.Jakobida"
return(Excavata.Discoba.Jakobida)
}
```

Haptophyta.Phaeocystis
```{r}
Haptophyta.Phaeocystis<-function(){
Haptophyta.Phaeocystis <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Haptophyta.Phaeocystis")
Haptophyta.Phaeocystis <- Haptophyta.Phaeocystis[3]
colnames(Haptophyta.Phaeocystis)<-"Haptophyta.Phaeocystis"
return(Haptophyta.Phaeocystis)
}
```





IT CANT FIND IT FOR SOME REASON
Haptophyta.non-Phaeocystis
```{r}
# Haptophyta.non-Phaeocystis <- Metagenome_Graph_data_alphabetical %>% 
#   filter(Taxa == "Haptophyta.non-Phaeocystis")
# Haptophyta.non-Phaeocystis <- Haptophyta.non-Phaeocystis[3]
# colnames(Haptophyta.non-Phaeocystis)<-"Haptophyta.non-Phaeocystis"
```

Opisthokonta.Holozoa
```{r}
Opisthokonta.Holozoa<-function(){
Opisthokonta.Holozoa <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Opisthokonta.Holozoa")
Opisthokonta.Holozoa <- Opisthokonta.Holozoa[3]
colnames(Opisthokonta.Holozoa)<-"Opisthokonta.Holozoa"
return(Opisthokonta.Holozoa)
}
```

Opisthokonta.otherOpisthokonta
```{r}
Opisthokonta.otherOpisthokonta<-function(){
Opisthokonta.otherOpisthokonta <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Opisthokonta.otherOpisthokonta")
Opisthokonta.otherOpisthokonta <- Opisthokonta.otherOpisthokonta[3]
colnames(Opisthokonta.otherOpisthokonta)<-"Opisthokonta.otherOpisthokonta"
return(Opisthokonta.otherOpisthokonta)
}
```

Picozoa.otherPicozoa
```{r}
Picozoa.otherPicozoa<-function(){
Picozoa.otherPicozoa <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Picozoa.otherPicozoa")
Picozoa.otherPicozoa <- Picozoa.otherPicozoa[3]
colnames(Picozoa.otherPicozoa)<-"Picozoa.otherPicozoa"
return(Picozoa.otherPicozoa)
}
```



Picozoa.Picomonadida
```{r}
Picozoa.Picomonadida<-function(){
Picozoa.Picomonadida <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Picozoa.Picomonadida")
Picozoa.Picomonadida <- Picozoa.Picomonadida[3]
colnames(Picozoa.Picomonadida)<-"Picozoa.Picomonadida"
return(Picozoa.Picomonadida)
}
```
	
	
	
Alveolata.Dinoflagellata
```{r}
Alveolata.Dinoflagellata<-function(){
Alveolata.Dinoflagellata <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Alveolata.Dinoflagellata")
Alveolata.Dinoflagellata <- Alveolata.Dinoflagellata[3]
colnames(Alveolata.Dinoflagellata)<-"Alveolata.Dinoflagellata"
return(Alveolata.Dinoflagellata)
}
```


Alveolata.otherAlveolata
```{r}
Alveolata.otherAlveolata<-function(){
Alveolata.otherAlveolata <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Alveolata.otherAlveolata")
Alveolata.otherAlveolata <- Alveolata.otherAlveolata[3]
colnames(Alveolata.otherAlveolata)<-"Alveolata.otherAlveolata"
return(Alveolata.otherAlveolata)
}
```


Rhizaria.Cercozoa
```{r}
Rhizaria.Cercozoa<-function(){
Rhizaria.Cercozoa <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Rhizaria.Cercozoa")
Rhizaria.Cercozoa <- Rhizaria.Cercozoa[3]
colnames(Rhizaria.Cercozoa)<-"Rhizaria.Cercozoa"
return(Rhizaria.Cercozoa)
}
```


Rhizaria.otherRhizaria
```{r}
Rhizaria.otherRhizaria<-function(){
Rhizaria.otherRhizaria <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Rhizaria.otherRhizaria")
Rhizaria.otherRhizaria <- Rhizaria.otherRhizaria[3]
colnames(Rhizaria.otherRhizaria)<-"Rhizaria.otherRhizaria"
return(Rhizaria.otherRhizaria)
}
```


SAR_unclassified
```{r}
SAR_unclassified<-function(){
SAR_unclassified <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "SAR_unclassified")
SAR_unclassified <- SAR_unclassified[3]
colnames(SAR_unclassified)<-"SAR_unclassified"
return(SAR_unclassified)
}
```


Stramenopiles.MAST-2
```{r}
Stramenopiles.MAST_2<-function(){
Stramenopiles.MAST_2 <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.MAST-2")
Stramenopiles.MAST_2 <- Stramenopiles.MAST_2[3]
colnames(Stramenopiles.MAST_2)<-"Stramenopiles.MAST-2"
return(Stramenopiles.MAST_2)
}
```


Stramenopiles.MAST-3
```{r}
Stramenopiles.MAST_3<-function(){
Stramenopiles.MAST_3 <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.MAST-3")
Stramenopiles.MAST_3 <- Stramenopiles.MAST_3[3]
colnames(Stramenopiles.MAST_3)<-"Stramenopiles.MAST-3"
return(Stramenopiles.MAST_3)
}
```


Stramenopiles.Diatomea.Bacillariophytina
```{r}
Stramenopiles.Diatomea.Bacillariophytina<-function(){
Stramenopiles.Diatomea.Bacillariophytina <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Diatomea.Bacillariophytina")
Stramenopiles.Diatomea.Bacillariophytina <- Stramenopiles.Diatomea.Bacillariophytina[3]
colnames(Stramenopiles.Diatomea.Bacillariophytina)<-"Stramenopiles.Diatomea.Bacillariophytina"
return(Stramenopiles.Diatomea.Bacillariophytina)
}
```


	
Stramenopiles.Diatomea.Coscinodiscophytina
```{r}
Stramenopiles.Diatomea.Coscinodiscophytina<-function(){
Stramenopiles.Diatomea.Coscinodiscophytina <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Diatomea.Coscinodiscophytina")
Stramenopiles.Diatomea.Coscinodiscophytina <- Stramenopiles.Diatomea.Coscinodiscophytina[3]
colnames(Stramenopiles.Diatomea.Coscinodiscophytina)<-"Stramenopiles.Diatomea.Coscinodiscophytina"
return(Stramenopiles.Diatomea.Coscinodiscophytina)
}
```


Stramenopiles.Diatomea.otherDiatomea
```{r}
Stramenopiles.Diatomea.otherDiatomea<-function(){
Stramenopiles.Diatomea.otherDiatomea <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Diatomea.otherDiatomea")
Stramenopiles.Diatomea.otherDiatomea <- Stramenopiles.Diatomea.otherDiatomea[3]
colnames(Stramenopiles.Diatomea.otherDiatomea)<-"Stramenopiles.Diatomea.otherDiatomea"
return(Stramenopiles.Diatomea.otherDiatomea)
}
```


Stramenopiles.Diatomea.ME-Euk-FW10
```{r}
Stramenopiles.Diatomea.ME_Euk_FW10<-function(){
Stramenopiles.Diatomea.ME_Euk_FW10 <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Diatomea.ME-Euk-FW10")
Stramenopiles.Diatomea.ME_Euk_FW10 <- Stramenopiles.Diatomea.ME_Euk_FW10[3]
colnames(Stramenopiles.Diatomea.ME_Euk_FW10)<-"Stramenopiles.Diatomea.ME-Euk-FW10"
return(Stramenopiles.Diatomea.ME_Euk_FW10)
}
```

Stramenopiles.Dictyochophyceae.Dictyochales
```{r}
Stramenopiles.Dictyochophyceae.Dictyochales<-function(){
Stramenopiles.Dictyochophyceae.Dictyochales <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Dictyochophyceae.Dictyochales")
Stramenopiles.Dictyochophyceae.Dictyochales <- Stramenopiles.Dictyochophyceae.Dictyochales[3]
colnames(Stramenopiles.Dictyochophyceae.Dictyochales)<-"Stramenopiles.Dictyochophyceae.Dictyochales"
return(Stramenopiles.Dictyochophyceae.Dictyochales)
}
```

Stramenopiles.Dictyochophyceae.otherDictyochophyceae
```{r}
Stramenopiles.Dictyochophyceae.otherDictyochophyceae<-function(){
Stramenopiles.Dictyochophyceae.otherDictyochophyceae <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Dictyochophyceae.otherDictyochophyceae")
Stramenopiles.Dictyochophyceae.otherDictyochophyceae <- Stramenopiles.Dictyochophyceae.otherDictyochophyceae[3]
colnames(Stramenopiles.Dictyochophyceae.otherDictyochophyceae)<-"Stramenopiles.Dictyochophyceae.otherDictyochophyceae"
return(Stramenopiles.Dictyochophyceae.otherDictyochophyceae)
}
```

Stramenopiles.Dictyochophyceae.Florenciellales
```{r}
Stramenopiles.Dictyochophyceae.Florenciellales<-function(){
Stramenopiles.Dictyochophyceae.Florenciellales <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Dictyochophyceae.Florenciellales")
Stramenopiles.Dictyochophyceae.Florenciellales <- Stramenopiles.Dictyochophyceae.Florenciellales[3]
colnames(Stramenopiles.Dictyochophyceae.Florenciellales)<-"Stramenopiles.Dictyochophyceae.Florenciellales"
return(Stramenopiles.Dictyochophyceae.Florenciellales)
}
```

Stramenopiles.Dictyochophyceae.Pedinellales
```{r}
Stramenopiles.Dictyochophyceae.Pedinellales<-function(){
Stramenopiles.Dictyochophyceae.Pedinellales <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Dictyochophyceae.Pedinellales")
Stramenopiles.Dictyochophyceae.Pedinellales <- Stramenopiles.Dictyochophyceae.Pedinellales[3]
colnames(Stramenopiles.Dictyochophyceae.Pedinellales)<-"Stramenopiles.Dictyochophyceae.Pedinellales"
return(Stramenopiles.Dictyochophyceae.Pedinellales)
}
```

	
Stramenopiles.Ochrophyta.other
```{r}
Stramenopiles.Ochrophyta.other<-function(){
Stramenopiles.Ochrophyta.other <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Ochrophyta.other")
Stramenopiles.Ochrophyta.other <- Stramenopiles.Ochrophyta.other[3]
colnames(Stramenopiles.Ochrophyta.other)<-"Stramenopiles.Ochrophyta.other"
return(Stramenopiles.Ochrophyta.other)
}
```

Stramenopiles.Phaeophyceae
```{r}
Stramenopiles.Phaeophyceae<-function(){
Stramenopiles.Phaeophyceae <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.Phaeophyceae")
Stramenopiles.Phaeophyceae <- Stramenopiles.Phaeophyceae[3]
colnames(Stramenopiles.Phaeophyceae)<-"Stramenopiles.Phaeophyceae"
return(Stramenopiles.Phaeophyceae)
}
```


Stramenopiles.otherStramenopiles
```{r}
Stramenopiles.otherStramenopiles<-function(){
Stramenopiles.otherStramenopiles <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Stramenopiles.otherStramenopiles")
Stramenopiles.otherStramenopiles <- Stramenopiles.otherStramenopiles[3]
colnames(Stramenopiles.otherStramenopiles)<-"Stramenopiles.otherStramenopiles"
return(Stramenopiles.otherStramenopiles)
}
```


Eukaryota;other
```{r}
Eukaryota_other<-function(){
Eukaryota_other <- Metagenome_Graph_data_alphabetical %>% 
  filter(Taxa == "Eukaryota;other")
Eukaryota_other <- Eukaryota_other[3]
colnames(Eukaryota_other)<-"Eukaryota;other"
return(Eukaryota_other)
}
```




