---
title: "Time_Course2"
author: "Idan Siman-Tov"
date: '2022-06-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(xlsx)
library(ggplot2)
library(ggfortify)
library(tidyverse)
library(dplyr)
library(GGally)
library(corrgram)
library(janitor)
library(reshape2)
library(ggpubr)
library(ggnewscale)





source("..//..//Functions//My_Functions.R")
source("..//..//Functions//medium_consolidation_functions//data_for_pca_formating_updatedSept2022_no_percentage_medium_consolidation.R")
source("..//..//Functions//medium_consolidation_functions//metagenome_taxa_removed_updatedSept2022_no_percentage_medium_consolidation.R")

source("..//..//Functions//medium_consolidation_functions//Taxa_DF_updatedSept2022_no_percentage_medium_consolidation.R")

```


```{r}
data_for_pca<-data_for_pca()
metagenome_taxa<-metagenome_taxa_removed()
```


```{r}
metagenome_taxa_percentage <-Percentage_Function(metagenome_taxa)
```




```{r}
# Format the table for ggplot
metagenome_taxa_count_time_course<-setNames(melt(metagenome_taxa), c('Taxa', 'Date', 'Percent_of_Population'))
metagenome_taxa_percentage_time_course<-setNames(melt(metagenome_taxa_percentage), c('Taxa', 'Date', 'Percent_of_Population'))
```




```{r}
# Convert numbers to log base 10 so that its easier to graph
# Converting Percent_of_Population to logs
metagenome_taxa_count_time_course_log<- metagenome_taxa_count_time_course
metagenome_taxa_count_time_course_log$Percent_of_Population<-log10(metagenome_taxa_count_time_course_log$Percent_of_Population)


# Converting percentages to logs
metagenome_taxa_percentage_time_course_log<- metagenome_taxa_percentage_time_course
metagenome_taxa_percentage_time_course_log$Percent_of_Population<-log10(metagenome_taxa_percentage_time_course_log$Percent_of_Population)

```




```{r}

# Filtering to only include the "Group 1" from percentages
Group_1_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Archaeplastida.Chlorophyta.and.otherArchaeplastida|Stramenopiles.Diatomea.ME-Euk-FW10|Stramenopiles.Dictyochophyceae.Pedinellales"))

# Filtering to only include the "Group 2" from percentages
Group_2_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Excavata.Discoba.Jakobida|Haptophyta.non_Phaeocystis|Eukaryota;other"))

# Filtering to only include the "Group 3" from percentages
Group_3_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Picozoa.Picomonadida"))

# Filtering to only include the "Group 4" from percentages
Group_4_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Rhizaria.Cercozoa|Stramenopiles.Dictyochophyceae.Dictyochales.and.Florenciellales.and.otherDictyochophyceae|Stramenopiles.MAST-2.and.MAST-3|Stramenopiles.Ochrophyta.other"))

# Filtering to only include the "Group 5" from percentages this is the group with no corolation
Group_5_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Alveolata.Dinoflagellata|Haptophyta.Phaeocystis|Stramenopiles.Phaeophyceae|Cryptophyceae.Geminigera.and.otherCryptophyceae|Stramenopiles.Diatomea.Bacillariophytina.and.Coscinodiscophytina.and.otherDiatomea|SAR_unclassified.and.otherStramenopiles.and.otherAlveolata"))
```



```{r}
# Graphing the time course


# Percent
 ggplot(Group_1_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
    geom_line(size=1.4) +
    ggtitle("Group_1_metagenome_taxa_percentage_time_course_log") +
    theme(axis.text = element_text(angle = -45))

# Percent
 ggplot(Group_2_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
    geom_line(size=1.4) +
    ggtitle("Group_2_metagenome_taxa_percentage_time_course_log") +
    theme(axis.text = element_text(angle = -45))

# Percent
 ggplot(Group_3_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
    geom_line(size=1.4) +
    ggtitle("Group_3_metagenome_taxa_percentage_time_course_log") +
    theme(axis.text = element_text(angle = -45))

# Percent
ggplot(Group_4_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("Group_4_metagenome_taxa_percentage_time_course_log") +
  theme(axis.text = element_text(angle = -45))

# Percent
ggplot(Group_5_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("Group_5_metagenome_taxa_percentage_time_course_log") +
  theme(axis.text = element_text(angle = -45))

```



```{r}
# Filtering to only include the "Group 2" from percentages
# All_metagenome_taxa_percentage_time_course_log <- metagenome_taxa_percentage_time_course_log %>% filter(str_detect(Taxa, "Excavata.Discoba.Jakobida|Haptophyta.non_Phaeocystis|Eukaryota_other"))

# Percent
 ggplot(metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
    geom_line(size=1.4) +
    ggtitle("All_metagenome_taxa_percentage_time_course_log") +
    theme(axis.text = element_text(angle = -45))
```







Heat map

```{r}
Date<-data.frame(
    Date= c("2012-11-27","2013-02-08","2013-12-27","2014-01-23","2014-02-03","2014-02-10","2014-02-28","2014-03-04","2014-12-01","2014-12-11","2015-01-12","2015-01-19","2015-02-09","2015-02-23","2015-03-09"))
```

```{r}
Enviromental_data<- cbind(Date,data_for_pca)
```

```{r}
Enviromental_data<-t(Enviromental_data)
```

```{r}
Enviromental_data<-janitor::row_to_names(Enviromental_data, 1, TRUE)
```

```{r}
Enviromental_data_melt<-setNames(melt(Enviromental_data), c('Enviromental', 'Date', 'Value'))

```

```{r}
Enviromental_data_melt[,3]<- sapply(Enviromental_data_melt[,3], as.numeric)
```






Temperature...C.
orangered2

Conductivity..S.m.
yellow2

Pressure..dbar.
dodgerblue

Fluorescence..mg.m³.
limegreen

Salinity
gold2

Depth..m.
darkblue

Density..kg.m³.
deepskyblue3

Chlorophyll..mg.m³.
seagreen

Phaeopigment..mg.m³.
lightseagreen

Phosphate..µmol.L.
slateblue

Silicate..µmol.L.
chartreuse3

Nitrite.and.Nitrate..µmol.L.
firebrick2

Primary.Prod...mg.m³.day.
coral2

Prim.Prod.STD..mg.m³.day.










group 1 with primary production and phosphate

```{r}
Group_1_time_course<- ggplot(Group_1_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("Group_1_metagenome_taxa_percentage_time_course_log") +
  theme(axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
       axis.title.x=element_blank()) 
      
```

```{r}
Group_1_time_heatmap<-ggplot() +
  
  # Stramenopiles.Diatomea.ME-Euk-FW10, Stramenopiles.Dictyochophyceae.Pedinellales with temp
  geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Temperature...C."), aes(x = Date, y = Enviromental, fill = Value)) +
  scale_fill_gradient2(low = "white", mid = "orangered2", high = "darkslategrey", midpoint = 0.5, name = "Temperature...C.") +
  new_scale_fill()+

  
  
  #  # Stramenopiles.Diatomea.ME-Euk-FW10 with Conductivity..S.m.
  # geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Conductivity..S.m."), aes(x = Date, y = Enviromental, fill = Value)) +
  # scale_fill_gradient2(low = "white", mid = "yellow2", high = "darkslategrey", midpoint = 2.8, name = "Conductivity..S.m.") +
  # new_scale_fill()+ 
 
  
  # Stramenopiles.Diatomea.ME-Euk-FW10, Stramenopiles.Dictyochophyceae.Pedinellales with Salinity
  geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Salinity"), aes(x = Date, y = Enviromental, fill = Value)) +
  scale_fill_gradient2(low = "white", mid = "gold2", high = "darkslategrey", midpoint = 33, name = "Salinity") +
  new_scale_fill()+
    
  
  
  # Stramenopiles.Diatomea.ME-Euk-FW10 and Stramenopiles.Dictyochophyceae.Pedinellales with Density..kg.m³
  geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Density..kg.m³."), aes(x = Date, y = Enviromental, fill = Value)) +
  scale_fill_gradient2(low = "white", mid = "deepskyblue3", high = "darkslategrey", midpoint = 1027, name = "Density..kg.m³.") +
  new_scale_fill()+
  
  
  
  # Archaeplastida.Chlorophyta.and.otherArchaeplastida with phospate
  geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Phosphate..µmol.L."), aes(x = Date, y = Enviromental, fill = Value)) +
  scale_fill_gradient2(low = "white", mid = "slateblue", high = "darkslategrey", midpoint = 1.5, name = "Phosphate..µmol.L.") +
  new_scale_fill()
  


```



problems with legend adjustments
```{r}
ggarrange(Group_1_time_course, Group_1_time_heatmap, heights = c(2, 1), ncol = 1, nrow = 2, align = "hv", hjust = 20)
```















group 2 with primary production and phosphate

```{r}
Group_2_time_course<- ggplot(Group_2_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("Group_2_metagenome_taxa_percentage_time_course_log") +
  theme(axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
       axis.title.x=element_blank()) 
      
```

```{r}
Group_2_time_heatmap<-ggplot() +
  
  # Stramenopiles.Diatomea.ME-Euk-FW10, Stramenopiles.Dictyochophyceae.Pedinellales with temp
  geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Temperature...C."), aes(x = Date, y = Enviromental, fill = Value)) +
  scale_fill_gradient2(low = "white", mid = "orangered2", high = "darkslategrey", midpoint = 0.5, name = "Temperature...C.") +
  new_scale_fill()+

  
  
   # Stramenopiles.Diatomea.ME-Euk-FW10 with Conductivity..S.m.
  geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Conductivity..S.m."), aes(x = Date, y = Enviromental, fill = Value)) +
  scale_fill_gradient2(low = "white", mid = "yellow2", high = "darkslategrey", midpoint = 2.8, name = "Conductivity..S.m.") +
  new_scale_fill()+
 
  

  new_scale_fill()
  


```



problems with legend adjustments
```{r}
ggarrange(Group_2_time_course, Group_2_time_heatmap, heights = c(2, 1), ncol = 1, nrow = 2, align = "hv", hjust = 20)
```






















Temperature...C.
orangered2

Conductivity..S.m.
yellow2





group 3 with temp and conductivity

```{r}
Group_3_time_course<- ggplot(Group_3_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("Group_3_metagenome_taxa_percentage_time_course_log") +
  theme(axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
       axis.title.x=element_blank()) 
      
```

```{r}
Group_3_time_heatmap<-ggplot() +
  
  # Picozoa.Picomonadida and temp
  geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Temperature...C."), aes(x = Date, y = Enviromental, fill = Value)) +
  scale_fill_gradient2(low = "white", mid = "orangered2", high = "darkslategrey", midpoint = 0.5, name = "Temperature...C.") +
  new_scale_fill()#+

# # Picozoa.Picomonadida and Conductivity..S.m.
# geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Conductivity..S.m."), aes(x = Date, y = Enviromental, fill = Value)) +
# scale_fill_gradient2(low = "white", mid = "yellow2", high = "darkslategrey", midpoint = 2.8, name = "Conductivity..S.m.") +
# new_scale_fill()

```

```{r}
ggarrange(Group_3_time_course, Group_3_time_heatmap, heights = c(2, 0.5), ncol = 1, nrow = 2, align = "hv", hjust = 10)+
      theme(plot.margin = margin(0,0,50,0, "pt")) 
```





group 4 with Primary.Prod...mg.m³.day.

```{r}
Group_4_time_course<- ggplot(Group_4_metagenome_taxa_percentage_time_course_log, aes(x=Date, y=Percent_of_Population, group=Taxa, color=Taxa)) +
  geom_line(size=1.4) +
  ggtitle("Group_4_metagenome_taxa_percentage_time_course_log") +
  theme(axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
       axis.title.x=element_blank()) 
      
```

```{r}
Group_4_time_heatmap<-ggplot() +
  
  # Rhizaria.Cercozoa and primary production
  geom_raster(data = filter(Enviromental_data_melt, Enviromental == "Primary.Prod...mg.m³.day."), aes(x = Date, y = Enviromental, fill = Value)) +
  scale_fill_gradient2(low = "white", mid = "coral2", high = "darkslategrey", midpoint = 450, name = "Primary.Prod...mg.m³.day.") +
  new_scale_fill()

```

```{r}
ggarrange(Group_4_time_course, Group_4_time_heatmap, heights = c(2, 0.5), ncol = 1, nrow = 2, align = "hv", hjust = 10)
```










